### 2016-09-20 Thesis/DCG_sb-wi-thesis-template/frontmatter/abstract.tex
draft to committee

\textbf{FIXME:  basically a placeholder; do not believe}

I did some research, read a bunch of papers, published a couple myself, (pick one):
\begin{enumerate}
	\item ran some experiments and made some graphs,
	\item proved some theorems
\end{enumerate}
and now I have a job.  I've assembled this document in the last couple of months so you will let me leave.  Thanks!

>>>>

\textbf{Abstract}

The 26S proteasome is the central proteolytic effector in the ubiquitin system that is responsible for degrading numerous regulators following their selective ubiquitylation. The 26S proteasome is made up of two distinct subcomplexes,
 the Regulatory Particle (RP), responsible for recognizing and unfolding ubiquitylated substrates, and the Core Protease (CP), responsible for degrading the unfolded polypeptide. 
Herein, I developed an affinity purification of the 26S proteasome that targeted the RP via two isoforms of the RPT4 subunit. With this newly developed affinity purification, in conjunction with a preivously developed CP-based affinity purification of 26S proteasome, I was able to selectively enrich for either the RP or CP subcomplexes.
Mass spectrometric analyses of these affinity purified complexes identify a large collection of interacting proteins that associate with either the core protease (CP) or regulatory particle (RP).
While much is known about the construction of the yeast and mammalian particles, little is known about the pathways used to assemble the plant particle.
Sequence comparisons, Y2H and BiFC studies revealed that some proteasome associated proteins are likely assembly chaperones, with several CP factors harboring a signature C-terminal HbYX motif that typically enables association with the $\alpha$-subunit ring.
Several of the RP-specific factors appear to be orthologs of the chaperones Nas2, Nas6, Hsm3.
Whereas yeast assembles only a single particle type, mammals can assemble alternate proteasomes isotypes by replacing individual subunits with distinct isoforms (e.g., immunoproteasomes).
In plants, most 26S proteasome subunits are encoded by paralogous genes with sufficient divergence to suggest that plants also accumulate a collection of particles.
However, proteomic analysis of proteasomes selectively enriched using paralog-specific tags strongly imply that although plants possess this genetic diversity, the incorporation of these paralogs appears random.
Taken together, these proteomic studies provide the first insights into plant proteasome assembly and diversity, and identify factors that may build the CP and RP subcomplexes and finally the 26S holo-particle.

### 2016-09-20 Thesis/DCG_sb-wi-thesis-template/frontmatter/acks.tex
draft to committee

\begin{wbepi}{Isaac Asimov (1988)}
Science doesn't purvey absolute truth. Science is a mechanism, a way of trying to improve your knowledge of nature. It's a system for testing your thoughts against the universe and seeing whether they match. This works not just for the ordinary aspects of science, but for all of life.
\end{wbepi}

Acknowledgements go here.

>>>>

\begin{wbepi}{Isaac Asimov (1988)}
Science doesn't purvey absolute truth. Science is a mechanism, a way of trying to improve your knowledge of nature. It's a system for testing your thoughts against the universe and seeing whether they match. This works not just for the ordinary aspects of science, but for all of life.
\end{wbepi}
	To my family, especially my wife Erin: I am forever grateful for your love and support, without which I would not be here today. The many adventures that we have already had are just the start of many more yet to come. To my parents, for instilling a curiosity in me that cannot be quenched, and for their unconditional love and support. To my father, Robert: for encouraging me to pursue the computational side of science and to my mother, Terri: for always encouraging me to teach others. To my brother, Aaron, for our many discussions, on science, life, and playing games. To my twin, Stephen, for always reminding me to have fun. To my good friend, Lucas, for all of your guidance and support when I was completely lost in code.

	My scientific colleagues and mentors, you have pushed me to become a better scientist and to always examine the world with a critical eye. Rick Vierstra, thank you for always pushing me, and helping me realize that we can always improve. Patrick Masson, thank you for providing a welcoming home during a time of change.

	I owe much of my mentorship to the Vierstra Lab. Richard Marshall, you are a great friend, and a great mentor. Without your guidance, I would have been lost. To Nick Gladman, for always listening to my crazy ideas, and for being a great friend. To Aaron Lomax, and Robb Stankey for your companionship while drinking coffee.

	I will always look back on my time in Madison fondly. To my friends, Richard, Kurt, Carol, and others: thank you for always being there.

### 2016-09-20 Thesis/DCG_sb-wi-thesis-template/intro/UPS.tex
draft to committee

\subsection{19S Regulatory Particle Assembly – RP Lid}
	Several modules and chaperones are involved in the assembly of the RP base; however, construction of the RP lid is not well understood. RP lid assembly has primarily been investigated in yeast by mutant analyses of specific RP lid subunits including mutants in Rpn7, Rpn9 and Rpn12 \citep{fukunaga10}. MS/MS analyses of affinity purified lid complexes in these differing mutant backgrounds identified two different subassemblies, the first containing Rpn5, 6, 8, 9, and 11, and the second containing Rpn3, Rpn7, and Sem1 \citep{fukunaga10}. Intriguingly, Sem1 was found to act as a bridge between Rpn3, and Rpn7, as cleavage of an engineered version of Sem1 containing a Tobacco Etch Virus (TEV)-cleavage site showed defects in RP lid assembly \citep{tomko14}. While Sem1 may play a role in proteasome biogenesis, alternative roles for Sem1 have been proposed.  In the mature particle, Sem1 has been found to aide in recognition of ubiquitin chains which are linked at lysine 48 or 63 \citep{paraskevopoulos14}. Proteasomes affinity purified from Sem1 mutants had only mild defects in stability, suggesting that its main function may be that of ubiquitin recognition \citep{paraskevopoulos14}.

>>>>

\subsection{19S Regulatory Particle Assembly – RP lid}
	Several modules and chaperones are involved in the assembly of the RP base; however, construction of the RP lid is not well understood. RP lid assembly has primarily been investigated in yeast by mutant analyses of specific RP lid subunits including mutants in Rpn7, Rpn9 and Rpn12 \citep{fukunaga10}. MS/MS analyses of affinity purified lid complexes in these differing mutant backgrounds identified two different subassemblies, the first containing Rpn5, 6, 8, 9, and 11, and the second containing Rpn3, Rpn7, and Sem1 \citep{fukunaga10}. Intriguingly, Sem1 was found to act as a bridge between Rpn3, and Rpn7, as cleavage of an engineered version of Sem1 containing a Tobacco Etch Virus (TEV)-cleavage site showed defects in RP lid assembly \citep{tomko14}. While Sem1 may play a role in proteasome biogenesis, alternative roles for Sem1 have been proposed.  In the mature particle, Sem1 has been found to aide in recognition of ubiquitin chains which are linked at lysine 48 or 63 \citep{paraskevopoulos14}. Proteasomes affinity purified from Sem1 mutants had only mild defects in stability, suggesting that its main function may be that of ubiquitin recognition \citep{paraskevopoulos14}.
